\begin{pgroup}{Applications of Dependent Types}
    \smallpaper{chlipala2011certified}{General applications of Coq for both formal verification and dependently typed programming.}
    \smallpaper{Chlipala:2010:USM:1806596.1806612}{Details the design of a statically typed language focused on type level programming.}
    \smallpaper{Chugh:2012:DTJ:2398857.2384659}{Details the design of a dependent type system for JavaScript (based on the idea of refinement types)}
    \smallpaper{Augustsson98cayenne--}{Describes one of the first general purpose programming languages with dependent types.}
\end{pgroup}

\begin{pgroup}{Dependent Type Theory}
  \smallpaper{pisigma}{Describes the design and implementation of a small dependently typed language for instruction purposes.}
  \smallpaper{Bunder_variantsof}{A survey of the variations on the Calculus of Constructions}
  \smallpaper{martinlof}{The original work on Martin-Lof style type theory.}
  \smallpaper{coctr}{The original paper describing the calculus of constructions, a dependent, pure type system.}
  \smallpaper{Altenkirch:2007:OE:1292597.1292608}{\makered{TODO}}
  \smallpaper{Abel08verifyinga}{\makered{TODO}}
  \smallpaper{Chugh:2012:NRL:2103656.2103686}{Describes the design of a nested refinement system for typing the features that exist in
  dynamic scripting languages.}
  \smallpaper{DBLP:journals/corr/abs-1103-5055}{Describes System D, a type system for typing very dynamic program behaviors using a novel technique
  for discharging proof obligations, to automate checking via an SMT solver.}
\end{pgroup}

\begin{pgroup}{Linear Types}
  \smallpaper{Wadler90lineartypes}{\makered{TODO}}
  \smallpaper{Wadler:2012:PS:2364527.2364568}{\makered{TODO}}
\end{pgroup}

\begin{pgroup}{Misc Type Theory}
    \smallpaper{Benton:1998:CTL:969611.969614}{\makered{TODO}}
    \smallpaper{Benton:2005:TCL:2099708.2099741}{\makered{TODO}}
\end{pgroup}
